A quantitative framework for investigating the reliability of empirical network construction: supplemental information

### 2019-01-16 manuscript/supplemental.tex
a few Dom comments that refer to newly-SI material

        The obvious rule of thumb to reduce uncertainty is ``sample more". Where resources permit, increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L_{ij} = 1$ but process or detection uncertainty is high). Despite these benefits, we note that there are limits to the utility of increased sampling. Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig. 2C, main text). While this improves our understanding of the set of species present in the community, it introduces yet more uncertainty into the interaction matrix. Note that it is better to identify the set of potential interactions than to miss a species, so sampling effort should not be reduced in order to exclude rare species.

>>>>

        The obvious rule of thumb to reduce uncertainty is ``sample more". Where resources permit, increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L_{ij} = 1$ but process or detection uncertainty is high). Despite these benefits, we note that there are limits to the utility of increased sampling. Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present~\citep{Gravel2018}), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig. 2C, main text). While this improves our understanding of the set of species present in the community, it introduces yet more uncertainty into the matrix of feasible interactions. Note that it is better to identify the set of potential interactions than to miss a species, so sampling effort should not be reduced in order to exclude rare species.
